Generalised Management Strategy Evaluation: modelling biodiversity and food security

### 2019-01-04 notebook/presentation/GMSE_presentation.Rmd
Up to gmse_apply in presentation

@@

@@

>>>>

One function [shows](https://confoobio.github.io/gmse/reference/plot_gmse_results.html) the general results of simulation dynamics.

@@

Another function [shows](https://confoobio.github.io/gmse/reference/plot_gmse_effort.html) manager permissiveness, and stakeholder effort, for each action.

@@

```{r, echo = FALSE}
renderDataTable(
    if(is.null(sim$data) == FALSE){
        dat <- gmse_table(sim$data)
        dat[,1:6];
    }
)
```

## Custom sub-models with gmse_apply {.smaller}

Custom models can be integrated into GMSE with `gmse_apply`, which [takes the arguments](https://confoobio.github.io/gmse/reference/gmse_apply.html) `res_mod`, `obs_mod`, `man_mod`, and `use_mod`.

Consider a logistic growth model:

$$N_{t+1} = N_{t} + rN_{t+1}\left(1 - \frac{N_{t}}{K}\right)$$

Written as a function in R to take in values from $N_{t}$ and return $N_{t+1}$.

```{r}
logistic_res_mod <- function(N_0, K = 2000, gr = 1){
    N_1 <- N_0 + gr * N_0 * ( 1 - N_0/K );
    return(N_1);
}

mod_result <- logistic_res_mod(N_0 = 200, gr = 0.3);
```

```{r, echo = FALSE}
print(mod_result);
```

The above function *and all of its arguments* can be integrated into `gmse_apply`.

## Custom sub-models with gmse_apply {.smaller}

```{r, echo = FALSE}
mod <- gmse_apply(res_mod = function(N_0 = 200, K = 2000, gr = 0.3) N_1 <- N_0 + gr * N_0 * ( 1 - N_0/K ), stakeholders = 5);
```

```{r, eval = FALSE}
mod <- gmse_apply(res_mod = logistic_res_mod, # Custom model
                  N_0 = 200, gr = 0.3,        # Custom arguments
                  stakeholders = 5);          # GMSE arguments
```

```{r, echo = FALSE}
print(mod);
```
